---
title: |
    | _Introduction 2 Next Generation Sequencing_
author: "Alex Sanchez-Pla"
date: "April 2021"
output:
 prettydoc::html_pretty:
    toc: true
    toc_depth: 3
    theme: architect
    highlight: github
    number_sections: true
editor_options: 
  chunk_output_type: console
  bibliography: references.bib
# link-citations: yes
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, comment = NA, prompt = TRUE, tidy = FALSE, fig.width = 7, fig.height = 7, fig_caption = TRUE,cache=FALSE)
Sys.setlocale("LC_TIME", "C")
```

```{r packages, include=FALSE}
# require(devtools)
# if(!require(installifnot)) install_github("uebvhir/installifnot")

library("bibtex")
```

# Motivació

Perquè parlem de seqüenciació

## Remember the _Omics Cascade_

## From genome to infinity, and beyond

## Genome sequencing

## The Human Genome Project

## To Understand something, sequence it (Ana Conesa)

# Evolució de les tecnologies de seqüenciació (un altre cop)

## El cost de la seqüenciació

https://www.genome.gov/about-genomics/fact-sheets/Sequencing-Human-Genome-cost

## La capacitat de seqüenciació

# Overview of sequencing technologies

## Sanger Sequencing

## 2nd Next Generation technologies: From Sanger to NGS

## Comparison 1- Library construction vs in vivo amplification

## Comparison 2 - Array (paralel) based sequencing

## The sequencing process in detail (1) Library preparation

## The sequencing process in detail (2) Clonal Amplification

## The sequencing process in detail (3) Cyclic Sequencing

## (2nd GS) Platforms

## 3rd Generation Sequencing

## (3rd GS) Platforms

## Platforms comparison

## Sequencing generations face to fac: Sanger vs NGS vs 3rd Gen



